Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-02-27 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/orb-grid.pdf}
   \caption{
        \textbf{I think show your work may have borked this? The vertical arrow and the one at the top look like they got squished?} The scattering phase angles accessible to a direct imaging mission can be limited by orbital inclination or by the coronagraphic inner working angle. 
        If the orbital inclination is close to face-on (top panels) then the scattering phase angles probed throughout an orbit are limited by inclination; for circular orbits accessible scattering phases are $\phi \in 90^\circ \pm i$. 
        For orbital inclinations close to edge-on (bottom panels) the planet goes through all phases, but the scattering phase angles near 0$^\circ$ and 180$^\circ$ are not accessible due to obscuration by the coronagraph mask; for circular orbits, the accessible scattering phases are $\phi \in 90^\circ \pm \arcsin({\rm IWA}\cdot d_*/a)$.
    }
    \label{fig:orb-grid}
    \script{plot-orb-grid.py}
\end{figure*}

>>>>

\begin{figure}%[t]
   \centering
   \includegraphics[width=0.99\columnwidth]{figures/orb-grid.pdf}
   \caption{
        The scattering phase angles accessible to a direct imaging mission can be limited by orbital inclination or by the coronagraphic inner working angle. 
        If the orbital inclination is close to face-on (top panels) then the scattering phase angles probed throughout an orbit are limited by inclination; for circular orbits accessible scattering phases are $\phi \in 90^\circ \pm i$. 
        For orbital inclinations close to edge-on (bottom panels) the planet goes through all phases, but the scattering phase angles near 0$^\circ$ and 180$^\circ$ are not accessible due to obscuration by the coronagraph mask; for circular orbits, the accessible scattering phases are $\phi \in 90^\circ \pm \arcsin({\rm IWA}\cdot d_*/a)$.
    }
    \label{fig:orb-grid}
    \script{plot-orb-grid.py}
\end{figure}
